A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model

### 2024-11-04 paper/paper.qmd
merged changes

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

Pollster

Population Type

Poll Regency (old if data collected in 30 days, old to capture regent old

Separated =between

@@

\[NTD: ADD MORE DETAILS ABOUT METHODOLOGY\] To allocate the \$100,000 budget, I would budget \$20,000 for a survey platform subscription to handle a large amount of data. I would put \$50,000 into advertising and recruitment for targeted digital ads and phone surveys. I will also use \$20,000 for data analysts and poll aggregation services and \$10,000 for re-contact surveys, contingency costs, and other miscellaneous costs. However, I believe \$100,000 is on the lower end to ensure a high-quality poll and will most likely cost more. Regardless, most of the costs will come from collecting the data, and I have budgeted for this reality (ADD CITATION).

\[NTD: ADD THIS AS ANOTHER SECTION\] Please find the proposed question list for the online survey attached here (INSERT URL).

>>>>

### Type of Pollster {sec-data-pollster}

The pollster variable was selected to consider the effect of changes in pollster on the observed variable. The pollster variable represents the polling organization that conducted the poll. The distribution of polling counts for different pollsters in @fig-pollster suggests that the data is dominated by three pollsters: Ipsos, YouGov and Siena/NYT. Further analysis is needed in their polling methodology to determine potential biases.

```{r}
#| label: tbl-pollster
#| fig-cap: Number of unique high-quality polling organizations
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

# Calculate summary statistics for the 'pollster' variable
summary_stats <- prediction %>%
  summarize(
    Pollster = n_distinct(pollster),
  )

# Display the summary statistics in a nicely formatted table
summary_stats %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

```{r}
#| label: fig-pollster
#| fig-cap: Distribution of high-quality polling organizations
#| echo: false
#| fig-width: 5 
#| fig-align: center

# Plot distribution using histogram
ggplot(prediction, aes(x = pollster)) +
  geom_bar(fill = "blue", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Pollster",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Population Type {sec-data-populationtype}

Population Type distinguishes among different groups surveyed into two groups surveyed: voters and adults. Adults is a more general poll that includes voters, likely voters and non-voters. @fig-populationtype shows that majority of the polls surveyed voters rather than the general adult population. The discrepancy between number of polls who surveyed voters and adults could introduce potential biases in responses, as those who are voters may have stronger opinions than those who are not.

```{r}
#| label: tbl-populationtype
#| fig-cap: Number of unique high-quality polling organizations
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

# Calculate summary statistics for the 'population' variable
summary_stats <- prediction %>%
  summarize(
    Population = n_distinct(population),
  )

# Display the summary statistics in a nicely formatted table
summary_stats %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

```{r}
#| label: fig-populationtype
#| fig-cap: Distribution of population type 
#| echo: false
#| fig-width: 5 
#| fig-align: center

# Plot distribution of Population Type using histogram
ggplot(prediction, aes(x = population)) +
  geom_bar(fill = "orange", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Population",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Poll Recency {sec-data-pollrecency}

Poll Recency, shown through the variable `recent_poll`, suggests that

- lot more older datapoints

Population Type distinguishes among different groups surveyed into two groups surveyed: voters and adults. Adults is a more general poll that includes voters, likely voters and non-voters. @fig-populationtype shows that majority of the polls surveyed voters rather than the general adult population. The discrepancy between number of polls who surveyed voters and adults could introduce potential baises in responses, as those who are voters may have stronger opinions than those who are not.

```{r}
#| label: tbl-recency
#| fig-cap: Number of polls that were collected within 30 days and after
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

# Calculate summary statistics for the 'population' variable
summary_stats <- prediction %>%
  summarize(
    Population = n_distinct(recent_poll),
  )

# Display the summary statistics in a nicely formatted table
summary_stats %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

```{r}
#| label: fig-recency
#| fig-cap: Distribution of on the amount of polls collected in 30 days 
#| echo: false
#| fig-width: 5 
#| fig-align: center

# Plot distribution of Population Type using histogram
ggplot(prediction, aes(x = recent_poll)) +
  geom_bar(fill = "purple", alpha = 0.7, color = "black") +
  theme_minimal() +
  labs(x = "Poll Recency",
       y = "Count") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

@@

To allocate the $100,000 budget, I would budget \$20,000 for a survey platform subscription to handle a large amount of data. I would put \$50,000 into advertising and recruitment for targeted digital ads and phone surveys. I will also use \$20,000 for data analysts and poll aggregation services and \$10,000 for re-contact surveys, contingency costs, and other miscellaneous costs. However, I believe \$100,000 is on the lower end to ensure a high-quality poll and will most likely cost more. Regardless, most of the costs will come from collecting the data, and I have budgeted for this reality.

Please find the proposed question list for the online survey attached here (INSERT URL).
